Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex
Update on Overleaf.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotLQ-cora-brute}
\caption{Linkage quality using brute-force linking on the Cora dataset\label{fig-cora-brute}}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/skye-mtree}
\caption{Linkage quality on Skye dataset using M-tree\label{skye-quality-mtree}}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/kili-mtree}
\caption{Linkage quality on Kilmarnock dataset using M-tree\label{kilmarnock-quality-mtree}}
\end{subfigure}
\caption{M-Tree based linkage on the demographic data sets}
\label{demography-quality-mtree}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
\caption{Comparison of quality attainable on Skye dataset using M-tree and various LSH configurations\label{mtree-lsh-quality}}
\end{figure}

>>>>

% \begin{figure}
% \includegraphics[width=\textwidth]{figures/plotLQ-cora-brute}
% \caption{Linkage quality using brute-force linking on the Cora dataset\label{fig-cora-brute}}
% \end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/skye-mtree}
\caption{Linkage quality on Skye dataset using M-tree\label{skye-quality-mtree}}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/kili-mtree}
\caption{Linkage quality on Kilmarnock dataset using M-tree\label{kilmarnock-quality-mtree}}
\end{subfigure}

\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-skye-f}
\caption{F-Measure values of all LSH variations vs M-Tree for the Skye data set}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotFs-kilmarnock-f}
\caption{F-Measure values of all LSH variations vs M-Tree for the Kilmarnock data set}
\end{subfigure}

\caption{Linkage results on the demographic data set}
\label{demography-quality-mtree}
\end{figure}

% \begin{figure}
% \includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
% \caption{Comparison of quality attainable on Skye dataset using M-tree and various LSH configurations\label{mtree-lsh-quality}}
% \end{figure}
